### 2018-07-16 paper/security-discussion.tex
WIP on security discussion, makes it compile

@@

Bob constructs \iac{SPOR} route that he gives to Alice.
This means that Alice does not learn any of Bob's destination devices.
When Alice starts sending the message, she will not connect directly to the 
device at the head of the route, since that might be Bob's device.
Alice will construct her own \ac{SPOR} route.
Thus Alice's devices are hidden from Bob's observation and vice versa.
If we assume that Alice and Bob can sample their nodes uniformly randomly from 
the \emph{entire} global set of devices %Global Device Retinue 
(we will return to this assumption 
below), then their probability of successful attack is proportional to their 
size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).

@@

If we choose \(\Enc*\) as a universal re-encryption~\cite{UniversalReencryption} 
scheme (possibly composed with the deniable, authenticated encryption above), 
then we could also provide bitwise unlinkability for the message between hops on 
the route.
(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
re-encryption of \(m\) before forwarding the message to the next hop.)
Without universal re-encryption, the message \(m\) itself remains constant 
throughout the route and thus constitutes a tag for tracking.
As long as \emph{at least one node on the route is honest}, \ie actually 
performs the re-encryption --- there is no incentive for them to do this, as 
neither Alice nor Bob can detect cheating without talking directly to each other 
to compare the ciphertexts --- then the link between Alice and Bob is broken.
This means that Carol and David must control all nodes on the route to link 
Alice's transfer to Bob.
As above, if we assume uniformly random peer sampling, then Carol and David's 
success probability is proportional to their joint size in the network.

>>>>

\paragraph*{Security of Sphinxes}

\dots

\paragraph*{Security of \acs*{SPOR}}

@@

Bob constructs \iac{SPOR} route that he gives to Alice.
Due to the properties that Sphinxes inherits from Sphinx, this means that Alice 
does not learn any of Bob's destination devices.
When Alice starts sending the message, she will not connect directly to the 
device at the head of the route, since that might be Bob's device.
Alice will construct her own \ac{SPOR} route.
Thus Alice's devices are hidden from Bob's observation and vice versa.
If we assume that Alice and Bob can sample their nodes uniformly randomly from 
the \emph{entire} global set of devices %Global Device Retinue 
(we will return to this assumption 
below), then their probability of successful attack is proportional to their 
size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).

@@

If we choose \(\Enc*\) as a universal re-encryption~\cite{UniversalReencryption} 
scheme (possibly composed with the deniable, authenticated encryption above), 
then we could also provide bitwise unlinkability for the message between hops on 
the route.
%(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
%re-encryption of \(m\) before forwarding the message to the next hop.)
Without universal re-encryption, the message \(m\) itself remains constant 
throughout the route and thus constitutes a tag for tracking.
As long as \emph{at least one node on the route is honest}, \ie actually 
performs the re-encryption --- there is no incentive for them to do this, as 
neither Alice nor Bob can detect cheating without talking directly to each other 
to compare the ciphertexts --- then the link between Alice and Bob is broken.
This means that Carol and David must control all nodes on the route to link 
Alice's transfer to Bob.
As above, if we assume uniformly random peer sampling, then Carol and David's 
success probability is proportional to their joint size in the network.
